% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.


% start a document with the here given default font size and paper size
\documentclass[10pt,a4paper]{article}

% include the `tex` instructions that takes care of loading packages and defining commands
\include{resume-commands}



\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins

\maintitle{Arjun Naik}{October 29, 1987}  % title on top of the document

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:Arjun.RN@gmail.com}{Arjun.RN\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{+}49-176-5788-6406
\\
\sbull
\href{https://de.linkedin.com/in/arnaik}{https://de.linkedin.com/in/arnaik}
\sbull
\href{https://github.com/arjunrn}{https://github.com/arjunrn}
\\
Berliner Allee 148\sbull
13088\sbull
Berlin\sbull
Germany

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing

\begin{multicols}{2}  % open a multicolumn environment
	Software engineer with 10+ years of experience in e-commerce and
	foundational systems. Has a passion for building features and functionality
	with a focus on reliability, scalability and maintainability. Established
	record of collaboration on large projects, mentorship of junior and
	mid-level engineers. Looking for positions in teams building critical
	systems with high performance, reliability requirements like security,
	infrastructure.
\end{multicols}

\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection
{\href{https://deliveryhero.com/}{Delivery Hero}}
{\textsc{Berlin, Germany}}
{
	\headedsubsection
	{\acr{Staff Software Engineer - Global Developer Platform}}
	{Aug 2022 - Current}
	{\bodytext{
			Development and steering of the self-service deployment tooling
			for users of the platform. Contributions to upstream AWS projects
			for managing AWS resources through Kubernetes resources.
			Integration of the in-house authentication/authorization solution into
			service mesh(Istio). Mentoring of engineers, design of systems in the
			domain and collaboration with other domains and entities.
		}
		\textbf{Technologies Used:} Go, Kubernetes, AWS controllers for Kubernetes, Open Application Model.
	}
}

\headedsection
{\href{https://redhat.com/}{Red Hat}}
{\textsc{Berlin, Germany}}
{
	\headedsubsection
	{\acr{Senior Software Engineer OpenShift}}
	{Jun 2021 - Jul 2022}
	{\bodytext{
			Developement of operators to extend the functionality of the
			OpenShift Container Platform through CRDs and controllers. Adding
			new features to the core OpenShift platform in the areas of
			networking and authentication and cluster upgrades.
		}
		\textbf{Technologies Used:} Go, OpenShift, controller-runtime, kubebuilder
	}
}

\headedsection
{\href{https://redhat.com/}{Red Hat}}
{\textsc{Berlin, Germany}}
{
	\headedsubsection
	{\acr{Senior Software Engineer SRE}}
	{Jul 2020 - May 2021}
	{\bodytext{
			Development and standardization of operators used to managed
			Openshift Dedicated clusters. Improving the monitoring of features
			used in OSD clusters.
		}
		\textbf{Technologies Used:} Go, OpenShift, Prometheus, controller-runtime, kubebuilder
	}
}

\headedsection
{\href{https://zalando.de/}{Zalando SE}}
{\textsc{Berlin, Germany}}
{
	\headedsubsection
	{\acr{Senior Software Engineer (AWS and Kubernetes) }}
	{Aug 2018 - June 2020}
	{\bodytext
		{
			Provided Kubernetes clusters and CI/CD integration to feature teams
			in Zalando to deploy their applications. Monitoring and upgrading
			the clusters so that teams can benefit from improved security and
			reliability.  Development of internal and opensource tooling for
			cluster users to deploy their applications seamlessly and perform
			application deployments with advanced features like pre-scaling,
			blue-green deployments and easy rollbacks. Improved autoscaling
			controllers in upstream Kubernetes projects so that user workloads
			can scale both vertically and horizontally. Other contributions to
			upstream Kubernetes open source projects.
		}
		\textbf{Technologies Used:} AWS, Go, Kubernetes, Ubuntu.
	}
}

\headedsection
{\href{https://cubits.com/}{Cubits}}
{\textsc{Berlin, Germany}}
{
	\headedsubsection
	{\acr{Site Reliability Engineer}}
	{Jan 2018 - May 2018}
	{\bodytext{
			Migration of the stack from baremetal to GKE clusters. Modified
			existing services to run on Kubernetes
		}
		\textbf{Technologies Used:} Google Compute Platform, Terraform, Helm,
		Prometheus.
	}
}

\headedsection
{\href{http://tech.zalando.com/}{Zalando SE}}
{\textsc{Berlin, Germany}}
{
	\headedsubsection
	{\acr{Software Engineer SRE}}
	{August 2015 - December 2017}
	{\bodytext{
			Part of the SRE team which worked with the feature teams in the
			migration of a monolithic codebase to microservices in the cloud.
			During this process of migration assisted teams in automating their
			deployments, instrumenting their applications for monitoring and
			performed load test to verify that the newly built services could
			satisy the performance and scaling requirements. Later moved to the
			Personalization department where I worked with the Recommendations
			team to deliver personalized item recommendations with Service
			Level Objectives(SLOs). Automating the deployments of the their
			infrastructure and implemented controllers and tooling to manage
			their datastores like Elasticsearch and Cassandra. Introduced
			monitoring for visualizing and observing the performance of various
			stages of the recommendations pipeline.
		}
		\textbf{Technologies Used:} Go, Java, AWS, locust, Spring Boot, Kubernetes,
		Elasticsearch, Cassandra.
	}
}

\headedsection
{\href{http://tu-dresden.de/die_tu_dresden/fakultaeten/fakultaet_informatik/sysa/se?set_language=en&cl=en}{TU Dresden}}
{\textsc{Dresden, Germany}}
{
	\headedsubsection
	{\acr{Wissenschaftliche Hilfskraft}}
	{Mar 2014 - Dec 2014}
	{\bodytext{
			As a part of the
			{\href{http://tu-dresden.de/die_tu_dresden/fakultaeten/fakultaet_informatik/sysa/se/srex}{SREX(Secure
			Remote Execution)}} project developed a translator for C programs
			which added redundancy to regular x86 instructions to detect and
			correct transient errors in memory and computation.  Also worked
			with consensus services like ZooKeeper and Consul to evalute their
			runtime characteristics. Implemented several new prototype features
			for a ZooKeeper client library.
		}
		\textbf{Technologies Used:} Python, Fabric, Apache ZooKeeper, C/C++,
		Scons, Consul, Mercurial
	}
}

\headedsection
{\href{http://dmfs.org/}{DMFS}}
{\textsc{Dresden, Germany}}
{
	\headedsubsection
	{\acr{Application Developer}}
	{Jan 2013 - March 2014}
	{\bodytext{
			Developed a web based platform for the bulk retail of mobile apps.
			The service used OpenSSL to sign packaged apps and verified the
			source of the app sold through the platform. Also developed the
			Android SDK which integrates with existing third-party apps to
			leverage this functionality. This also included the task of
			building and maintaining the infrasturcture for deploying and
			running the platform.
		}
		\textbf{Technologies Used:} Python, Android, Django, OpenSSL,
		PostgreSQL, Git
	}
}

\headedsection
{\href{http://www.notiphi.com}{Locus Labs}}
{\textsc{Bangalore, India}}
{
	\headedsubsection
	{\acr{Web and Mobile Developer}}
	{Jun 2011 - August 2012}
	{\bodytext{
			Locus Labs was an early stage startup for providing location based
			advertising and services through mobile applications. Had to manage
			several resposibilities, from building the backend services,
			tinkering with the frontend code and also maintaing the deployment
			pipelines to make releases.
		}
		\textbf{Technologies Used:} Django, Python, Android, Tornado, Fabric,
		Scrapy, Javascript, JQuery, MySQL, MongoDB, Redis, Git
	}
}

\headedsection  % sets the header for the section and includes any subsections
{\href{http://www.netbramha.com}{Netbramha Studios}}
{\textsc{Bangalore, India}}
{
	\headedsubsection  % sets the header for a subsection and contains usually body text
	{\acr{Web Developer}}
	{Oct 2010 - May 2011}
	{\bodytext{
			Netbramha Studios is a design consultancy which develops aesthetic
			and content intensive websites. Handled the technical aspects list
			aaintenance of websites and minor front-end development. Also built
			websites using both third-party and in-house server frameworks.
			Used JQuery for front-end development and also did some basic
			layout and styling with \acr{HTML+CSS}.
		}
		\textbf{Technologies Used:} PHP, CodeIgniter, CakePHP, JQuery,
		Javascript, Python, Django, SVN, Git}
}

\begin{center}
	\emph{Please consult my \href{https://de.linkedin.com/in/arnaik}{LinkedIn Profile} for references.}
\end{center}

\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
{Techniche Universit{\"a}t Dresden}
{\textsc{Dresden, Germany}} {%
	\headedsubsection
	{Master of Science, Distributed Systems Engineering}
	{Oct 2012 -- Mar 2015}
	{\bodytext{
			Completed courses in Security and Cryptography, Software Fault
			Tolerance and Dependable Systems. Also worked in the Systems
			Engineering Lab and Software Fault Tolerance Lab. Under the guidance
			of Prof. Dr. Christof Fetzer completed my Master's Thesis in scaling
			Zookeeper. The thesis proposed a solution which partitioned the
			Zookeeper FS namespace to shard the data and increase the throughput
			by reducing the overhead of the consensus algorithm.
		}
	}
}

\headedsection
{BM Sreenivasaiah College of Engineering, Vivesvararya Technological University}
{\textsc{Bangalore, India}} {%
	\headedsubsection
	{Bachelor of Computer Science and Engineering}
	{Jul 2006 -- Apr 2010}
	{\bodytext{
			Major in Computer Science with a focus on Computer Architecture. Was
			also an editor of the departmental newsletter and a regular
			contributor.  For my final year project developed a Wi-Fi enabled
			robot which could be controlled over the Internet.
		}
	}
}

\spacedhrule{1.6em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
{Technical Skills:}
{
  Software design and architecture, Linux internals(particularly containers and
  networking), databases, REST APIs. Proficient in Go and Python with some
  background in Java and C/C++.
}
\end{document}
